Reply To Examiners

### 2014-03-31 answer_thesis_examiner/answer_document.tex
auto

It is partially for the second concern that log-transformation is proposed.
Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$.

@@

>>>>

It is partially for the second concern that log-transformation is proposed.
Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below.

@@

The Examiner also expresses his concern about the quality of the ``visual match'' on page 66.
For this, I had updated the section to include a quantitative, and hence objective, measure of match instead of the current subjective evaluation.
I believe, such a change should completely addresses his concerns.
I also made other small updates, to addresses his other various minor concerns.

\subsubsection*{7. Chapter 5}

Page 94, section 5.2.2.2 is updated to indicate MSE as ``Mean Squared Error''.
The reference for computation in the section is the ``true signal'' $\sigma$.

Fig. 5.11 shows two curves that are essentially the same.
One of them is ``simulated result'' and the other is ``analysis formula''.
The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
The purpose is to show that the heuristic formula given as

\begin{align*}
  MSE = \frac{1}{(ENL-0.5)\ln^2(2)}
\end{align*}

closely tracks observable values.
Readers should also note that this argument is presented in a much more detailed manner in Section 5.3.2.1.
